%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{fixltx2e} % Used for SYN2cat (to subscript the 2/di)

%%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Steve}{Clement}{information technology and science mentor} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
45, rue G.D. Charlotte
Mersch, L-7520
Luxembourg
~
+352 691 20 33 66
~
%%\href{mailto:steve@localhost.lu}{steve@localhost.lu}
%%\href{http://www.SteveClement.lu}{http://SteveClement.lu}
%%\href{http://twitter.com/SteveClement}{tw://@SteveClement}
{steve@localhost.lu}
{http://SteveClement.lu}
{tw://@SteveClement}
{li://in/steveclement3}
\section{languages}
luxembourgish native
english, french \& german fluency
\section{programming}
{\color{red} $\varheartsuit$} Python
JavaScript, C++, PHP
CSS3 \& HTML5
\section{key skills}
Information Security
Unix \& System Administration
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}
\begin{entrylist}
%------------------------------------------------
\entry
{2010--Now}
{SMILE Security made in L\"{e}tzebuerg}
{Luxembourg}
{\emph{1\textsuperscript{st} Operational Core Security Team for the Nation at CIRCL} \\
Being part of the initial team for the national \\
\underline{C}omputer \underline{E}mergence \underline{R}esponse \underline{T}eam I am involved in all aspects of day to day incident handling procedures.\\
Detailed achievements:
\begin{itemize}
    \item Day to day incident management
    \begin{itemize}
        \item Evaluate risk
        \begin{itemize}
            \item Leak, 0-Day, Malware, Phish \ldots
        \end{itemize}
        \item Technical analysis
        \begin{itemize}
             \item Who owns that domain\/network\/malware
             \item Basic malware reverse engineering
        \end{itemize}
        \item Liaising with constituents
    \end{itemize}
    \item InfoSec trend watch, R\&D on various big data topics
\end{itemize}}
%------------------------------------------------
\entry
{2010--Now}
{National Public Radio 100,7}
{Luxembourg}
{\emph{Freelancer} \\
Monthly Radio shows on "Start-ups" and "Technologies"}
%------------------------------------------------
\entry
{2013--Now}
{Code Club}
{Luxembourg}
{\emph{co-founder} \\
With the obvious lack of any open and free technology teachings Code Club closes this gap with bringing computer programming to 7 - 18 year olds.}
%------------------------------------------------
\entry
{2008--Now}
{SYN\textsubscript{2}cat}
{Luxembourg}
{\emph{co-founder} \\
An open space where people of all ages can come and tinker not only with Technologies but also arts and crafts as well as have passionate discussions about the modern age we live in}
%------------------------------------------------
\entry
{2009-2012}
{agglomera}
{Luxembourg}
{\emph{Founder} \\
Information Security consulting Business for SME's}
%------------------------------------------------
\entry
{2002-2008}
{ION Network Solutions s.\`{a} r.l}
{Luxembourg}
{\emph{Founder} \\
Built a successful IT Services Company. Being involved in all levels of company creation and management}
%------------------------------------------------
\entry
{2000-2002}
{A.L Digital Ltd. // The Bunker Ltd.}
{United Kingdom, London}
{\emph{Junior Systems Administrator} \\
Junior position in a leading Internet Services Provider to built network infrastructure and server systems for small and medium entreprises}
%------------------------------------------------
\end{entrylist}

%%% Only force new-page if not enough content on experience page
\newpage

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}
\begin{entrylist}
%------------------------------------------------
\entry
{2001--2002}
{Studying BSc {\normalfont of Mathematics}}
{The Open University, United Kingdom, London}
{\emph{Studying BSc} \\ in Applied Mathematics, Pure Mathematics and the History of Mathematics.}
%------------------------------------------------
\entry
{1996--2000}
{Technical Regime}
{Lyc\'{e}e Technique des Arts et Metiers, Luxembourg}
{Program specializing in Information Technology}
%------------------------------------------------
\end{entrylist}



%----------------------------------------------------------------------------------------
%	TECH PROFICENCY
%----------------------------------------------------------------------------------------

\section{technology proficiency}

\begin{entrylist}
%------------------------------------------------
\entry
{*nix}
{Unix expert}
{}
{Expert level on any Unix flavor. Able to setup, maintain and extend complex high-availability setups.}
%------------------------------------------------
\entry
{\#InfoSec}
{Information Security expert}
{}
{Over 10 years of information security expertise being able to identify emerging threats and mitigation tactics to better secure infrastructures.}
%------------------------------------------------
\entry
{Coding \& Teaching}
{Versatile Mentor}
{}
{Since the advent of information security awareness raising for Luxembourg's schools being an experienced mentor to Kids and Young people was key. \\
Having co-founded Code Club Luxembourg reinforced this essential skill.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{teaching skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2008}
{Various Information Security Courses}
{Schools nation-wide}
{Literally toured the country to give the mentioned awareness raising courses from Lower- to Upper-schools Kids.}
%------------------------------------------------
\entry
{2008--Now}
{Talks}
{Various Conferences}
{Regular presentation on code in schools, information security and other topics on national as well as international conferences.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data analysis, entrepreneurship, economics, software design, marketing \\
\textbf{\ \ \ \ \ \ personal:} endurance sports (Triathlon), cooking, sociology, history, languages

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{publications}

%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

%\printbibsection{book}{books} % Print all books from the bibliography

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}

%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}