% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Templateqq
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{fixltx2e} % Used for SYN2cat (to subscript the 2/di)

%%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Steve}{Clement}{information security \& incident response expert} % Your name \& current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
133, rue de Reckenthal
L-2410, Strassen
Luxembourg
~
+352 691 20 33 66
~
%%\href{mailto:steve@localhost.lu}{steve@localhost.lu}
%%\href{http://www.SteveClement.lu}{http://SteveClement.lu}
%%\href{http://twitter.com/SteveClement}{tw://@SteveClement}
{steve@localhost.lu}
{http://SteveClement.lu}
{tw://@SteveClement}
{li://in/steveclement3}
\section{languages}
Luxembourgish native
English, French \& German fluency
Japanese student
\section{programming}
{\color{red} $\varheartsuit$} Python
JavaScript, PHP
CSS3 \& HTML5
C++, Swift
\section{key skills}
Information Security
Incident Response
Threat Intelligence
Information Sharing \& Planning
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}
\begin{entrylist}
%------------------------------------------------
\entry
{2010--Now}
{SMILE Security made in L\"{e}tzebuerg}
{Luxembourg}
{\emph{1\textsuperscript{st} Operational Core Security Team for Luxembourg} \\
Being part of the initial team for the national \\
\underline{C}omputer \underline{E}mergency \underline{R}esponse \underline{T}eam (CIRCL) I am involved in all aspects of day to day incident handling. Detailed achievements:
\begin{itemize}
    \item Day to day incident handling
    \begin{itemize}
        \item Risk assessment
        \begin{itemize}
        	\item Technical vs. non-Technical (e.g Physical breaches)
            \item Leaks; 0-Day; Malware; Phishing \ldots
        \end{itemize}
        \item Technical analysis
        \begin{itemize}
             \item Who owns that domain/network/malware
             \item Basic malware reverse engineering
        \end{itemize}
        \item Liaising with constituents
    \end{itemize}
    \item InfoSec trend watch, R\&D on various big data topics
\end{itemize}}
%------------------------------------------------
\entry
{2010--Now}
{National Public Radio 100,7}
{Luxembourg}
{\emph{Freelancer} \\
Monthly section on Startups, Technologies.}
%------------------------------------------------
\entry
{2014--Now}
{CoderDojoLu}
{Luxembourg}
{\emph{Founder} \\
CoderDojo teaches every Thursday computer science \& other technologies to 7 - 18 year olds, free of charge, in Bonnevoie, Luxembourg.}
%------------------------------------------------
\entry
{2014--Now}
{Wearable Wednesday}
{Luxembourg}
{\emph{Founder} \\
Wearable Wednesdays are about the imminent shift of technology into our everyday life. Teach yourself how to make your own creations.}
%------------------------------------------------
\entry
{2013--Now}
{Code Club}
{Luxembourg}
{\emph{co-Founder} \\
With the obvious lack of any open \& free technology teachings, Code Club closes this gap with bringing computer programming to 7 - 18 year olds.}
%------------------------------------------------
\entry
{2008--Now}
{SYN\textsubscript{2}cat}
{Luxembourg}
{\emph{co-Founder} \\
Community driven Open-space where people of all ages can come \& tinker, not only with technologies but also arts, crafts \& the like.}
%------------------------------------------------
\entry
{2009-2012}
{\emph{a}gglomera}
{Luxembourg}
{\emph{Founder} \\
Information Security consulting business for SME's.}
%------------------------------------------------
\entry
{2002-2008}
{ION Network Solutions s.\`{a} r.l}
{Luxembourg}
{\emph{Founder} \\
Built a successful IT services company. Being involved in all levels of company creation \& management.}
%------------------------------------------------
\entry
{2000-2002}
{A.L Digital Ltd. // The Bunker Ltd.}
{United Kingdom, London}
{\emph{Junior Systems Administrator} \\
Junior position in a leading ISP to build network infrastructure \& HA systems for SME's.}
%------------------------------------------------
\end{entrylist}

%%% Only force new-page if not enough content on experience page
\newpage

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}
\begin{entrylist}
%------------------------------------------------
\entry
{2001--2002}
{Studying BSc {\normalfont of Mathematics}}
{The Open University, United Kingdom, London}
{\emph{Studying BSc} \\ in applied mathematics, pure mathematics \& the history of mathematics.}
%------------------------------------------------
\entry
{1996--2000}
{Technical Regime}
{Lyc\'{e}e Technique des Arts et Metiers, Luxembourg}
{Program specializing in Information Technology}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	TECH PROFICENCY
%----------------------------------------------------------------------------------------

\section{technology proficiency}

\begin{entrylist}
%------------------------------------------------
\entry
{*nix}
{Unix expert}
{}
{Expert level on any Unix flavor. Able to setup, maintain \& extend complex high-availability setups.}
%------------------------------------------------
\entry
{\#InfoSec}
{Information Security expert}
{}
{Over 10 years of information security expertise being able to identify emerging threats \& mitigation tactics to better secure infrastructures.}
%------------------------------------------------
\entry
{Coding \& \\ Teaching}
{Versatile Mentor}
{}
{Since the advent of information security awareness for Luxembourg's schools, being an experienced mentor to kids \& young people was key. \\
Having co-founded Code Club Luxembourg reinforced this essential skill. \\
With private code lessons as well as coding in primary schools of Luxembourg, I have a strong basis of classroom principles \& developing a fun, interactive student experience.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{teaching skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2008--Now}
{Presentations \& Workshops}
{Various Conferences}
{Regular presentation on code in schools, information security \& other topics on national as well as international conferences.}
%------------------------------------------------
\entry
{2008}
{Various Information Security Courses}
{Schools nation-wide}
{Literally toured the country to give the mentioned awareness raising courses to lower-/upper-schools kids.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data analysis, entrepreneurship, economics, software design, marketing \\
\textbf{\ \ \ \ \ \ personal:} endurance sports (triathlon), cooking, sociology, history, languages, wearables

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{publications}

%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

%\printbibsection{book}{books} % Print all books from the bibliography

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}

%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}
