% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Templateqq
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV (now defunct, 2021)
%
% Modified by:
% @SteveClement
% https://github.com/SteveClement/CV.git
% 
% Inspirations from: https://github.com/Nadorrano/cv-friggeri-x/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{fixltx2e} % Used for SYN2cat (to subscript the 2/di)
\usepackage{marvosym} % needed to print glyphs for email, cell phone etc.
%%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

% The followin enable CJK and needs for Japanese the fonts from: http://ipafont.ipa.go.jp/old/ipafont/download.html
\usepackage{zxjatype}
%\usepackage[ipa]{zxjafont}

\begin{document}

\header{Steve}{Clement}{Information Security \& incident response expert} % Your name \& current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
\pin \hfill 133, r. de Reckenthal
L-2410, Strassen
Luxembourg
~
{\Large\textcolor{gray}{\Mobilefone}} \hfill +352 20 33 66
{\Large\textcolor{gray}{\Letter}}\hfill\href{mailto:steve@localhost.lu}{steve@localhost.lu}
~
\tlogo \hfill \href{http://twitter.com/johnsmith}{@SteveClement}
\llogo \hfill \href{http://linkedin.com/johnsmith}{in://steveclement3}
\href{http://SteveClement.lu}{http://SteveClement.lu}
\section{languages}
Luxembourgish native
English, French \& German fluency
Japanese 学生
\section{programming}
{\color{red} $\varheartsuit$} Python
JavaScript, PHP
CSS3 \& HTML5
C++, Swift
\section{key skills}
Information Security
Incident Response
Threat Intelligence
Information Sharing \& Planning
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}
\begin{entrylist}
%------------------------------------------------
\entry{10'--Now}
{Security made in L\"{e}tzebuerg GIE}
{Luxembourg}
{\\
\emph{Senior Information Security Engineer} \\
\underline{C}omputer \underline{I}ncident \underline{R}esponse \underline{C}enter \underline{L}uxembourg (CIRCL)
\begin{itemize}
    \item Risk assessment
    \begin{itemize}
        \item Technical vs.\ non-Technical (e.g Physical breaches)
        \item Leaks; 0-Day; Malware; Phishing monitoring \ldots
    \end{itemize}
    \item Technical analysis
    \begin{itemize}
        \item Domain/network/malware ownership detection
        \item Basic malware reverse engineering
        \item Core MISP developer \& translation/documentation lead
    \end{itemize}
    \item Liaising with constituents
    \item InfoSec trend watch, R\&D on various big data topics
\end{itemize}
}
%------------------------------------------------
\entry{10'--2015}
{National Public Radio 100,7}
{Luxembourg}
{\emph{Freelancer}\\
Monthly section on Startups, Technologies.}
%------------------------------------------------
\entry{09'--2012}
{\emph{a}gglomera}
{Luxembourg}
{\emph{Founder}\\
Information Security consulting business for SME's.}
%------------------------------------------------
\entry{02'--2008}
{ION Network Solutions s.\`{a} r.l}
{Luxembourg}
{\emph{Founder} \\
Built a successful IT services company. Being involved in all levels of company creation \& management.}
%------------------------------------------------
\entry{00'--2002}
{A.L Digital Ltd. // The Bunker Ltd.}
{United Kingdom, London}
{\emph{Junior Systems Administrator} \\
Junior position in a leading ISP to build secure infrastructure \& HA systems for SME's.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	NOTABLE MISSIONS SECTION
%----------------------------------------------------------------------------------------

\section{missions}
\begin{entrylist}
%------------------------------------------------
\entry{March 2019}
{International Monetary Fund}
{IMF, Kyrgyz Republic}
{\emph{Technical lead} \\ for a capacity building mission for the National Kyrgyz central bank.}
%------------------------------------------------
\entry{March 2020}
{Alliance for Financial Inclusion}
{AFI, Malaysia, KL}
{\emph{Technical lead} \\ to train and explain the benefits and challenges of information sharing to the central bank governors of the AFI network members.}
%------------------------------------------------
\entry{17'--Now}
{APAC liason}
{Tokyo, Japan}
{Co-operation efforts between the Japanese CSIRT landscape (public and private) to ease the reaction times in case of cyberincidents between the continents.}
%------------------------------------------------
\entry{17'--Now}
{AUSCERT liason}
{Brisbane, AU}
{Direct contact point for the Australian CSIRT AUSCERT. CIRCL is a collaborator to help growth, adaptability and enabling AUSCERT to provide better services to its members.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%%% Only force new-page if not enough content on experience page
\newpage

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}
\begin{entrylist}
%------------------------------------------------
\entry{01'--2002}
{Studying BSc {\normalfont of Mathematics}}
{The Open University, United Kingdom, London}
{\emph{Studying BSc} \\ in applied mathematics, pure mathematics \& the history of mathematics.}
%------------------------------------------------
\entry{96'--2000}
{Technical Regime}
{Lyc\'{e}e Technique des Arts et Metiers, Luxembourg}
{Program specializing in Information Technology}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	TECH PROFICENCY
%----------------------------------------------------------------------------------------

\section{Technology proficiency}

\begin{entrylist}
%------------------------------------------------
\entry{*nix}{Unix expert}
{}
{Expert level on any Unix flavor. Able to setup, maintain \& extend complex high-availability setups.}
%------------------------------------------------
\entry{\#InfoSec}
{Information Security expert}
{}
{Over 10 years of information security expertise being able to identify emerging threats \& mitigation tactics to better secure infrastructures.}
%------------------------------------------------
\entry{\#Intel}
{Threat Intelligence expert}
{}
{MISP being one of the main platforms in the threat sharing landscape, being involved since 2002 when CIRCL took over the project, gives me a competitive advantage in understanding the underlying Technologies of the product. Further, having been exposed to various community building efforts, the knowledge of best practices has been further developed by my team and me, for the benefits of the greater community.}
%------------------------------------------------
\entry{Coding \& \\ Teaching}
{Versatile Mentor}
{}
{Since the advent of information security awareness for Luxembourg's schools, being an experienced mentor to kids \& young people was key. \\
Having co-founded Code Club Luxembourg reinforced this essential skill. \\
With private code lessons as well as coding in primary schools of Luxembourg, I have a strong basis of classroom principles \& developing a fun, interactive student experience.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Teaching skills}

\begin{entrylist}
%------------------------------------------------
\entry{08'--Now}
{Presentations \& Workshops}
{Various Conferences}
{Regular presentation on code in schools, information security \& other topics on national as well as international conferences.}
%------------------------------------------------
\entry{2008}
{Various Information Security Courses}
{Schools nation-wide}
{Literally toured the countries' public schools to give the mentioned awareness raising courses to lower-/upper-schools kids.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data analysis, entrepreneurship, economics, software design, marketing \\
\textbf{\ \ \ \ \ \ personal:} endurance sports, cooking, sociology, history, languages, japonology

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{publications}

%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

%\printbibsection{book}{books} % Print all books from the bibliography

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}

%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}
